---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# navigatr

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/navigatr)](https://CRAN.R-project.org/package=navigatr)
[![Codecov test coverage](https://codecov.io/gh/UchidaMizuki/navigatr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/UchidaMizuki/navigatr?branch=main)
[![R-CMD-check](https://github.com/UchidaMizuki/navigatr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/UchidaMizuki/navigatr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

navigatr provides navigation menus and input forms.

the navigation menu allows piped data processing for hierarchical data structures.
By activating menu items, operations on each item can be performed while maintaining the overall structure with attributes.

The core functions of this package are as follows,

- `new_nav_menu()` builds a new navigation menu.
  - `activate()` accesses a menu item.
- `new_nav_input()` builds a new input form.
  - `itemise()` enters values into the form.
- `rekey()` and `rekey_with()` renames the key of a menu item.

## Installation

You can install navigatr from CRAN.

``` r
install.packages("navigatr")
```

You can also install the development version from GitHub.

``` r
# install.packages("devtools")
devtools::install_github("UchidaMizuki/navigatr")
```

## Examples

```{r,message=FALSE, warning=FALSE}
library(navigatr)
library(dplyr)
```

### Build a navigation menu

To create a new navigation menu, give `new_menu()` unique keys and a list of their corresponding values.
The top rows show the menu items (keys on the left, value summaries on the right).
The `description` argument allows you to add descriptions to the menu items (optional).

```{r}
band <- new_nav_menu(
  key = c("band_members", "band_instruments"),
  value = list(
    band_members, 
    band_instruments
  ),
  description = c(
    "A data frame of band members",
    "A data frame of band instruments"
  )
)
band
```

You can activate a menu item by `activate()`.
Activating a menu item allows you to perform operations on the active item.
`activate()` turns a `navigatr_new_menu` object into an `navigatr_nav_item` object, and `deactivate()` turns it back.

```{r}
band <- band |>
  activate(band_members) |>
  filter(
    band == "Beatles"
  )
band
```

```{r}
band <- band |> 
  deactivate()
band
```

The `rekey()` function is used to change the key of an activated menu item.

```{r}
band |> 
  activate(band_instruments) |> 
  rekey("new_band_instruments")
```

You can also build a nested navigation menu.
To activate the items, specify multiple variables.

```{r}
bands <- new_nav_menu(
  key = c("key1", "key2"),
  value = list(band, band) # A list of menu objects
) 
bands |> 
  activate(key1, band_instruments) |> 
  select(name)
```

### Build a input form

```{r}
input <- new_nav_input(
  key = c("key1", "key2")
)
input
```

```{r}
input |> 
  itemise(
    key1 = "value1",
    key2 = "value2"
  )
```
